Instructions for COLING-2020 Proceedings

### 2020-07-21 paper/main.tex
Commiting after emoji table

@@

The goal of the $\corona$ dataset is to include any geolocated tweet that references the coronavirus in any language.
We use a relatively complicated process to extract these tweets in order to ensure maximum recall and precision in a wide range of languages.
Our procedure is:
\begin{enumerate}
\item
We generated a list of \XXX English-language search terms related to the coronavirus,
such as \texttt{coronavirus}, \texttt{covid19}, \texttt{wuhan} and \texttt{lockdown}.
We then used Bing's translation API to translate each of these terms into the 72 languages supported by Bing translate.
Table \ref{table:search_terms} in the supplemental material contains the full list of search terms in English and selected translations.
\item
We used Python's \texttt{spacy} library \citep{fixme} to tokenize and lemmatize each of the \XXX million tweets in the full dataset.
\texttt{spacy} supports this process in 58 different languages,
and for each tweet we used the appropriate \texttt{spacy} module for the language specified in the tweet's metadata.
\item
Finally, the $\corona$ dataset is constructed as the set of all tweets whose lemmatized text contains any of the search terms from the tweet's language or English.
We include both languages in this filtering step because it is common for non-English tweets to use English words like \texttt{coronavirus} when referencing the virus.
\end{enumerate}
Table \ref{table:lang} shows the 54 languages that are supported by all 3 services along with the total number of tweets in each language.
Figure \ref{fig:corona:perday} provides a summary of the number of tweets per day and Figure \ref{fig:corona:spatial} shows the spatial distribution of the tweets.

\begin{table}
    \centering
    \includegraphics[height=2in]{example-image-a}
    \caption{The number of tweets in each language.} 
    \label{table:lang}
\end{table}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{images/finalcountgraph1.eps}
    \caption{Number of tweets per day...}
    \label{fig:tweets_per_day}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[height=2in]{example-image-a}
    \caption{The spatial distribution of the dataset.}
    \label{fig:corona:spatial}
\end{figure}

@@

\begin{figure}
    %\includegraphics[width=0.4\textwidth]{images/Plutchik-wheel.png}
    \includegraphics[width=\textwidth]{images/emotions.eps}
    \caption{Results of sentiment analysis conducted using nvidia-sentiment on 170k tweets related with the corona outrbreak }
    \label{fig:nvidia-sentiment}
\end{figure}

@@

Following the work of \citet{fixme1,fixme2,fixme3}, we use emojis as distant labels for emotions.
Hand classifying text by emotions is an expensive and error prone process,
and the largest existing datasets for this task contain only about 10,000 tweets focusing on the limited domains of video games \citep{fixme} or stock performance \citep{fixme}.
The Unicode Standard \citep{fixme} currently defines over 3000 emojis,
most of which do not represent emotions.
In our analysis, we use only the original 80 emoji defined in the Unicode standard's emoticon code block (code points \texttt{0x1f600} - \texttt{0x1f650}).\footnote{
    In common usage, the words \defn{emoji} and \defn{emoticon} are interchangeable,
    but in this paper we adopt the Unicode Standard's definitions of these terms.
    By these definitions, an \defn{emoji} is any one of 3304 pictographs that are not part of any written language,
    and an \defn{emoticon} is one of the original 80 emoji.
}
We limit are analysis to emoticons only because:
they are the most commonly used emoji on twitter\footnote{
    See \url{http://www.emojitracker.com/} for realtime stats on Twitter emoji usage.
}
and each of these emoticons represents an emotion (emoticon is a portmanteau of emotion and icon).

To generate the $\emoticon$ dataset, 
we filtered the full set of geolocated tweets so that only tweets containing one of the 80 emoticons were included,
and any duplicate tweets were removed.
Then we preprocessed each tweet by replacing all user mentions with a special token \texttt{<mention>} and all URLs with a special token \texttt{<url>} and deleting all emojis.
We decided to keep all hashtags because hashtags can contain potentially valuable emotional content.
There exist a lot of tweets that contain multiple repetitions of emojis.
We address the issue similarly to how \cite{100 million tweets} did where for each unique emoji we have a separate tweet with that emoji as a label. 
For tweets containing repetitions of the same emoji; we only save one instance of it.
Finally, each tweet is labelled with the emojis that were deleted from the tweet.

In total, the $\emoticon$ dataset contains 64.2 million tweets sent by 4.2 million users,
and the tweets are written in 66 different languages and were sent from 246 different countries.
Table \ref{table:lang} shows the total number of tweets per language,
and Figure \ref{fig:emoticons} shows the full list of emoticons and their counts in our dataset.

\begin{figure}
    \centering
    \includegraphics[height=2in]{example-image-a}
    \caption{Emoticons image.}
    \label{fig:emoticons}
\end{figure}

@@

\section{Related Work}
\label{sec:related}
\subsection{Datasets:}
It is now worth mentioning previous datasets related with sentiment and emotion classification. The Sentiment Evaluation task 2018 \cite{SemEval2018Task1} presents a dataset of English, Arabic and Spanish tweets extracted from Twitter API, labelled for an array of subtasks on inferring the affectual state of a person from their tweet. Seventy-five teams submitted to one or more of the five total tasks; however, most of the submissions where for the language English. 
\cite{liu2019dens} introduces the DENS dataset, for multi-class emotion analysis. By collecting both English classic literature and modern online narratives, and by fine-tuning the pre-trained uncased BERT-large model to the multi-class passage classification task they achieved a micro-F1 average score of 60.4\%.
%\cite{liu2019dens}

@@

\subsection{Examples of large scale sentiment analysis:}
\cite{mohammad2015sentiment} explores both stance and sentiment analysis by providing a dataset of annotated tweet-target pairs, organized
a shared Task competition on Stance. Their stance detection system achieved an F-score of 70.3 \%, where they utilized an linear-kernel
SVM classifier. Their stance dataset contains 4k tweets, aimed towards topics such as Hillary Clinton, Atheism and etc. In addition,
\cite{yang2015twitter} provides an insight into measuring emotional contagion in Social Media. By using SentiStrengh (a sentiment analysis program),
and the findings of a study which claims that individuals are more likely to adopt positive or negative emotions if these are over-expressed in
their social network; the authors pursuit in establishing a relation between the sentiment of a tweet and that of the tweets that its author may have seen in a short
time period preceding its posting. Interestingly, they raise ethical concerns as they require massive-scale content manipulation with unknown consequences for the individuals therein involved.
Finally, the provide noteworthy limitations of observational experiments.
%\cite{mohammad2015sentiment}

@@

%\cite{yang2015twitter}
\subsection{Emoji Prediction:}
It is now worth mentioning previous work on Emoji Prediction. \cite{SemEval2018Task2} offered 2 subtasks for multilingual-emoji prediction: English and Spanish. By using Twitter API,
they located tweets either in the US (600k total) or in Spain (120k total). The tweets only included the one's with a single emoji and where limited to the top 20 emojis used across those countries. \cite{Tubingen Olso} achieved 
the best performance in both the English and Spanish Tweets: F1-Score: 35.99 \%, F1-Score: 22.36 \% respectively obtained by an SVM classifier with bag-of-n-grams features. One of the best performing teams 
\cite{NTUA-SLP}, achieved an F1-score of 35.36 \% on the English tweets, by using LSTM architecture with attention mechanism, initializing the embedding layer with word2vec and training end-to-end with back-propagation. 
The preprocessing tool they used was ekprahsis \cite{Baziotis} which contains social tokenizer aimed for social media, spell correction and word segmentation which can be used for hashtag segmentation. Finally, \cite{towards understanding creatieve lang}
explores both Irony Detection and the Emoji Prediction Task. They highlight that the knowledge the models gain is entirely from the corresponding training data, such training mechanism may work well for traditional text genres with formal sentences; however; 
it usually achieves an unsatisfiable performance with informal text, such as social media text.  By adopting a transfer learning model based on pretrained-BERT they achieved an F1-Score of 38.52 \% on the Emoji Prediction task. Issues raised by the authors were: overfitting 
due to the lack of more training data to fine-tune the system and time complexity.  
\section{Discussion}
\label{sec:discussion}
-Figure with number of tweets per language top 10? (Written Form) Twitter Emoticon
-Accuracies for BERT model with different hyper parameters and benchmarks 
-Twitter Corona a graph similar to what I did with the nvidia sent but for the emoji's top 10 
-Figure for correlation between plutchik wheel and emoji (the one you posted on github)
-Spatial distribution of the dataset

>>>>

%\usepackage{subfig}

@@

The goal of the $\corona$ dataset is to include any geolocated tweet that references the coronavirus in any language.
We use a relatively complicated process to extract these tweets in order to ensure maximum recall and precision in a wide range of languages.
Our procedure is:
\begin{enumerate}
\item
We generated a list of \XXX English-language search terms related to the coronavirus,
such as \texttt{coronavirus}, \texttt{covid19}, \texttt{wuhan} and \texttt{lockdown}.
We then used Bing's translation API to translate each of these terms into the 72 languages supported by Bing translate.
Table \ref{table:search_terms} in the supplemental material contains the full list of search terms in English and selected translations.
\item
We used Python's \texttt{spacy} library \citep{spacy2} to tokenize and lemmatize each of the \XXX million tweets in the full dataset.
\texttt{spacy} supports this process in 58 different languages,
and for each tweet we used the appropriate \texttt{spacy} module for the language specified in the tweet's metadata.
\item
Finally, the $\corona$ dataset is constructed as the set of all tweets whose lemmatized text contains any of the search terms from the tweet's language or English.
We include both languages in this filtering step because it is common for non-English tweets to use English words like \texttt{coronavirus} when referencing the virus.
\end{enumerate}
Table \ref{table:lang} shows the 54 languages that are supported by all 3 services along with the total number of tweets in each language.
Figure \ref{fig:corona:perday} provides a summary of the number of tweets per day and Figure \ref{fig:corona:spatial} shows the spatial distribution of the tweets.

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{images/finalcountgraph1}
    \caption{Number of tweets per day for hashtags related with coronavirus or the lockdown}
    \label{fig:tweets_per_day}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[height=2in]{distribution_countries.eps}
    \caption{The spatial distribution of the dataset.}
    \label{fig:corona:spatial}
\end{figure}

@@

\begin{table}
    \centering
    \includegraphics[height=2in]{distribution_lang.eps}
    \caption{The number of tweets in each language.} 
    \label{table:lang}
\end{table}

@@

Following the work of \citet{fixme1,fixme2,fixme3}, we use emojis as distant labels for emotions.
Hand classifying text by emotions is an expensive and error prone process,
and the largest existing datasets for this task contain only about 10,000 tweets focusing on the limited domains of video games \citep{fixme} or stock performance \citep{fixme}.
The Unicode Standard \citep{fixme} currently defines over 3000 emojis,
most of which do not represent emotions.
In our analysis, we use only the original 80 emoji defined in the Unicode standard's emoticon code block (code points \texttt{0x1f600} - \texttt{0x1f650}).\footnote{
    In common usage, the words \defn{emoji} and \defn{emoticon} are interchangeable,
    but in this paper we adopt the Unicode Standard's definitions of these terms.
    By these definitions, an \defn{emoji} is any one of 3304 pictographs that are not part of any written language,
    and an \defn{emoticon} is one of the original 80 emoji.
}
We limit are analysis to emoticons only because:
they are the most commonly used emoji on twitter\footnote{
    See \url{http://www.emojitracker.com/} for real-time stats on Twitter emoji usage.
}
and each of these emoticons represents an emotion (emoticon is a portmanteau of emotion and icon).

To generate the $\emoticon$ dataset, 
we filtered the full set of geolocated tweets so that only tweets containing one of the 80 emoticons were included,
and any duplicate tweets were removed.
Then we preprocessed each tweet by replacing all user mentions with a special token \texttt{<mention>} and all URLs with a special token \texttt{<url>} and deleting all emojis.
We decided to keep all hashtags because hashtags can contain potentially valuable emotional content.
There exist a lot of tweets that contain multiple repetitions of emojis.
We address the issue similarly to how \cite{100 million tweets} did where for each unique emoji we have a separate tweet with that emoji as a label. 
For tweets containing repetitions of the same emoji; we only save one instance of it.
Finally, each tweet is labelled with the emojis that were deleted from the tweet.
s
In total, the $\emoticon$ dataset contains 64.2 million tweets sent by 4.2 million users,
and the tweets are written in 66 different languages and were sent from 246 different countries.
Table \ref{table:lang} shows the total number of tweets per language,
and Figure \ref{fig:emoticons} shows the full list of emoticons and their counts in our dataset.

\begin{figure}%
    \centering
    \subfloat{{\includegraphics[scale=0.78]{./images/emojitable.pdf}}}%
    \label{adsad}
    \subfloat{{\includegraphics[scale =0.21]{emoticonwheel.jpg} }}%
    \caption{2 Figures side by side}%
    \label{fig:example}%
\end{figure}

@@

\section{Related Work}
\label{sec:related}
\subsection{Datasets:}
It is now worth mentioning previous datasets related with sentiment and emotion classification. The Sentiment Evaluation task 2018 \cite{mohammad-etal-2018-semeval} presents a dataset of English, Arabic and Spanish tweets extracted from Twitter API, labelled for an array of subtasks on inferring the affectual state of a person from their tweet. Seventy-five teams submitted to one or more of the five total tasks; however, most of the submissions where for the language English. 
\cite{liu2019dens} introduces the DENS dataset, for multi-class emotion analysis. By collecting both English classic literature and modern online narratives, and by fine-tuning the pre-trained uncased BERT-large model to the multi-class passage classification task they achieved a micro-F1 average score of 60.4\%.
%\cite{liu2019dens}

@@

\subsection{Examples of large scale sentiment analysis:}
\cite{mohammad2016stance} explores both stance and sentiment analysis by providing a dataset of annotated tweet-target pairs, organized
a shared Task competition on Stance. Their stance detection system achieved an F-score of 70.3 \%, where they utilized an linear-kernel
SVM classifier. Their stance dataset contains 4k tweets, aimed towards topics such as Hillary Clinton, Atheism and etc. In addition,
\cite{yang2015twitter} provides an insight into measuring emotional contagion in Social Media. By using SentiStrengh (a sentiment analysis program),
and the findings of a study which claims that individuals are more likely to adopt positive or negative emotions if these are over-expressed in
their social network; the authors pursuit in establishing a relation between the sentiment of a tweet and that of the tweets that its author may have seen in a short
time period preceding its posting. Interestingly, they raise ethical concerns as they require massive-scale content manipulation with unknown consequences for the individuals therein involved.
Finally, the provide noteworthy limitations of observational experiments.
%\cite{mohammad2015sentiment}

@@

%\cite{yang2015twitter}
\subsection{Emoji Prediction:}
It is now worth mentioning previous work on Emoji Prediction. \cite{barbieri-etal-2018-semeval} offered 2 subtasks for multilingual-emoji prediction: English and Spanish. By using Twitter API,
they located tweets either in the US (600k total) or in Spain (120k total). The tweets only included the one's with a single emoji and where limited to the top 20 emojis used across those countries. \cite{Tubingen Olso} achieved 
the best performance in both the English and Spanish Tweets: F1-Score: 35.99 \%, F1-Score: 22.36 \% respectively obtained by an SVM classifier with bag-of-n-grams features. One of the best performing teams 
\cite{baziotis-etal-2018-ntua-slp}, achieved an F1-score of 35.36 \% on the English tweets, by using LSTM architecture with attention mechanism, initializing the embedding layer with word2vec and training end-to-end with back-propagation. 
The preprocessing tool they used was ekprahsis \cite{baziotis-etal-2017-datastories-semeval} which contains social tokenizer aimed for social media, spell correction and word segmentation which can be used for hashtag segmentation. Finally, \cite{towards understanding creatieve lang}
explores both Irony Detection and the Emoji Prediction Task. They highlight that the knowledge the models gain is entirely from the corresponding training data, such training mechanism may work well for traditional text genres with formal sentences; however; 
it usually achieves an unsatisfiable performance with informal text, such as social media text.  By adopting a transfer learning model based on pretrained-BERT they achieved an F1-Score of 38.52 \% on the Emoji Prediction task. Issues raised by the authors were: overfitting 
due to the lack of more training data to fine-tune the system and time complexity.  
\section{Discussion}
\label{sec:discussion}
-Figure with number of tweets per language top 10? (Written Form) Twitter Emoticon
-Accuracies for BERT model with different hyper parameters and benchmarks 
-Twitter Corona a graph similar to what I did with the nvidia sent but for the emoji's top 10 
-Figure for correlation between plutchik wheel and emoji (the one you posted on github)
-Spatial distribution of the dataset
